\documentclass{article}
\title{How to Modify the E-Board Lineup on the Valpo ACM Website}
\date{}

\usepackage{minted}

\begin{document}
	\maketitle
	
	\begin{Large}
		\section{Why Would eboard.json Need Modified?}
	\end{Large}
	This file is extremely important to update. This file contains the data on the Valpo ACM E-Board members. It is vital that this file is up to date and accurate since this is what visitors of the website will see. 
	
	This file needs to be modified in accordance to any E-Board changes that happen either during the semester or after a new semester begins. E-Board elections are held on a yearly basis (sometimes in a semester depending on the circumstances). After the results of elections or other changes occur, this file should be modified as soon as possible. 
	
	\vspace{48pt}
	\begin{Large}
		\section{General Formatting}
	\end{Large} 
	
	\begin{minted}[breaklines, breakanywhere, frame=lines, framesep=5mm, linenos=true, tabsize=2]{json}
		{
			"members": [
				{
					"position": "Vice-President",
					"name": "Sam Thyen",
					"major": ["Computer Science"],
					"git": "https://github.com/EyeBrawler",
					"linkedin": "https://www.linkedin.com/in/samuel-thyen/"
				},
				{
					"position": "Treasurer",
					"name": "Max Kotelnikov",
					"major": ["Computer Science", "Data Science", "Mathematics"]
				},
				{
					"position": "Advisor",
					"name": "Nick Rosasco",
					"major": [],
					"git": "https://github.com/nsrosasco",
					"linkedin": "https://www.linkedin.com/in/nicholas-r-8aa83851/"
				}
			]
		}
	\end{minted}
	
	\subsection{"position"}
	The "position" property contains the position of each E-Board member. The potential positions include: 
	\begin{itemize}
		\item President
		\item Vice President
		\item Secretary
		\item Treasurer
		\item Public Relations Coordinator
		\item Webmaster
		\item Advisor
	\end{itemize}
	
	\subsection{"name"}
	The "name" property is very self explanatory. This value holds the name of an E-Board member. 
	
	\subsection{"major"}
	The "major" property is once again clear on what data is held in it. However, this property is an array. In most cases, only one major will be in the array. There are exceptions to this at times. In some cases, an E-Board member has more than one major. A case that always exists is for the organization advisor, who does not have a major since they already have a PhD. Both examples of this are shown in the example above. 
	
	\subsection{"git"}
	The "git" property holds a link for the E-Board member's GitHub link. This property is optional, which means it does not need to be included. Use the example above to see how that looks. 
	
	\subsection{"linkedin"}
	The "linkedin" property contains the link for an E-Board member's LinkedIn page. This property is also optional. The above example shows how that looks. 
\end{document}